### 2017-02-04 prob.tex
fresh changes

\section{Problem Setup}
We now present the linear programming (LP), approximate linear programming (ALP) and the generalized reduced approximate linear programming (GRLP) respectively. In what follows, $c>0\in \R^n$ is a probability distribution.
It is well known, the optimal value function $J^*$ can be obtained by solving the following linear program:
\begin{align}\label{mdplp}
\begin{split}
\min_{J\in \R^n}\, &c^\top J\,\,\text{s.t.}\\
%\mb
J(s)&\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'),\,\,
\forall (s,a)\in S\times A,
\end{split}
\end{align}
\begin{comment}
When the MDP has a large number of states, it is difficult to solve for $J^*$ using either the linear program \eqref{mdplp} or other full state representation methods such as value iteration or policy ite
ration \cite{BertB}. A practical solution is to resort to function approximation. Linear function approximation, wherein the solution is searched in the subspace spanned by the column vectors of a given feature matrix $\Phi$.\par
\end{comment}
The approximate linear program (ALP) is obtained by making use of LFA in the LP, i.e., by introducing the new variables $r\in \R^k$ and adding the extra constraint $J=\Phi r$ in \eqref{mdplp} with $\Phi \in \R^{n\times k}$ \citep{SchSei85}.
By substitution, this leads to
\begin{align}\label{alp}
\begin{split}
\min_{r\in \R^k}\, &c^\top \Phi r\,\,\,
\text{s.t.}\mb \Phi r\geq T \Phi r,
\end{split}
\end{align}
where $J\geq TJ$ is a shorthand for the $nd$ constraints in \eqref{mdplp} and $\Phi$ is a feature matrix whose first column is $\one$.
The Generalized Reduced Linear Program is given as:
\begin{align}\label{grlp}
\begin{split}
&\underset{r\in \N\subset R^k}{\min}\, \, c^\top \Phi r\,\,\,\,\\
&\text{s.t.}\mb  \,W^\top E\Phi r\geq W^\top H \Phi r,
\end{split}
\end{align}
Unless specified otherwise we use $\hr$/$\tr$ to denote an arbitrary solution to the GRLP/ALP. In similar spirit, and we let $\hj=\Phi \hr$/$\tj=\Phi \tr$ to denote the corresponding value functions and $\hu$/$\tu$ to denote the greedy policy w.r.t. $\hj$/$\tj$.\par
\textbf{Remarks:}
\begin{enumerate}
\item When the MDP has a large number of states, it is difficult to solve for $J^*$ using either the linear program \eqref{mdplp} or other full state representation methods such as value iteration or policy iteration \cite{BertB}. A practical solution is to resort to function approximation. Linear function approximation, wherein the solution is searched in the subspace spanned by the column vectors of a given feature matrix $\Phi$. For $k=n$ and $\Phi=I_{n\times n}$, the ALP is same as the LP.
\item $W \in \R^{nd\times m}_+$ is a matrix with all positive entries which specifies the linear combination of constraints. $\N$ is a compact set such that $\tr \in \N$. This additional constraint set ensures the boundedness of the solution. For $m=nd$ and $W=I_{nd\times nd}$, the GRLP is same as the ALP.
\end{enumerate}
\FloatBarrier
\input{cartoon}
\Cref{cartoon} which shows the solutions to the LP, ALP and GRLP respectively. The erorr in the ALP solution has already been studied in \cite{ALP}. Our objective is to study the extra source of error due to constriant approximation.
\begin{comment}
In addition, we answer the following questions related to constraint reduction in ALP that have so far remained open. \\
$\bullet$ As a natural generalization of the RLP, what happens if we define a generalized reduced linear program (GRLP) whose constraints are positive linear combinations of the original constraints of the ALP?\\
$\bullet$ Unlike \cite{CS} which provides error bounds for a specific RLP formulated using an idealized sampling distribution, is it possible to provide error bounds for any GRLP (and hence any RLP)?
In this paper, we address both of the questions above.
\end{comment}

>>>>

\section{Linear Programming for MDP}
In this section, we review relevant results \cite{BertB,ALP,CS} in the linear programming approach to MDPs. Throughout the rest of the paper, we let $c>0\in \R^n$ to denote a probability distribution over the state space S.\par
\begin{comment}
%first present linear programming (LP), approximate linear programming (ALP) and reduced linear programming (RLP) respectively. The LP is an exact method in that it computes $J^*$ and the other two methods (ALP and RLP) are approximate methods that are based on introducing LFA in LP. We then discuss prior literature that have analyzed the approximation errors in ALP and RLP. Finally, we present the open question that we wish to understand in this paper.
\end{comment}
\textbf{Linear Programming (LP)}: It is well known, the optimal value function $J^*$ can be obtained by solving the following linear program:
\begin{align}\label{mdplp}
&\text{LP:~}\min_{J\in \R^n}\,c^\top J\,\,\\
%\mb
&J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'),\,\,
\forall (s,a)\in S\times A,\nn
\end{align}
\textbf{Approximate Linear Programming (ALP)} is obtained by making use of LFA in the LP, i.e., by introducing the new variables $r\in \R^k$ and adding the extra constraint $J=\Phi r$ in \eqref{mdplp} with $\Phi \in \R^{n\times k}$ \citep{SchSei85}. By substitution, this leads to
\begin{flalign}\label{alp}
\begin{split}
\text{ALP:}& \min_{r\in \R^k}\, c^\top \Phi r\\
& \Phi r\geq T \Phi r,
\end{split}
\end{flalign}
where $J\geq TJ$ is a shorthand for the $nd$ constraints in \eqref{mdplp}. Note that, for $k=n$ and $\Phi=I_{n\times n}$, the ALP is same as the LP. In what follows, we use the notation $\tj=\Phi \tr$ and $\tu=u_{\tj}$ where $\tr\in\R^k$ denotes an arbitrary solution to ALP in \eqref{alp}.\par
A detailed theoretical analysis of ALP can be found in \cite{ALP}. However, we restate (from \cite{ALP}) a useful preliminary\footnote{The improved error bounds in \cite{ALP} as well as in \Cref{sec:improv} of this paper are in a weighted $L_\infty$ norm (see \Cref{notations}-\eqref{norms}).} performance bound for ALP as follows:
\begin{theorem}[Error Bound for ALP]\label{alpvanilla}
Let $\one\in \R^k$ belong to the column span of $\Phi$ and let $\mu_u\eqdef (1-\alpha)c^\top\top(I-\alpha P_u)^{-1}$ be a probability distribution over $S$ induced by a policy $u$. Then it follows that
\begin{enumerate}
\item\label{alppe} The prediction error is bounded as $||J^*-\tj||_{1,c}\leq \frac{2}{1-\alpha}\min_{r}||J^*-\Phi r||_\infty$.
\item\label{alpce} The control error is bounded as $||J^*-J_{\tu}||_{1,c}\leq \frac{2}{1-\alpha}||J^*-\tj||_{1,\mu_{\tu}}$.
\end{enumerate}
\end{theorem}
The gist of \Cref{alpvanilla}-\eqref{alppe} is that the prediction error $||J^*-\tj||_{1,c}$ of ALP is worse utmost by a constant factor than the best possible error that can be achieved using the span of $\Phi$. Further from \Cref{alpvanilla}-\eqref{alpce} the control error is worse utmost by a constant factor than the prediction error.\par
\textbf{Reduced Linear Programming (RLP)} is formulated by retaining only $m$ out of the $nd$ ($m<<nd$) constraints of ALP. RLP is easier to solve compared to ALP due to the reduced number of constraints.
\begin{align}\label{rlp}
\begin{split}
&\text{RLP:~}\underset{r\in \N\subset R^k}{\min}\, c^\top \Phi r\,\,\\
%\mb
&\Phi r (s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')\Phi r(s'),\,\,
\forall (s,a)\in \I,
\end{split}
\end{align}
where $\I\subset S \times A$ is the index set of sampled constraints, i.e., $|\I|=m$ and $\N$\footnote{The appendix explains how $\N$ can be chosen analytically.} is a compact set such that $\tr \in \N$, and it ensures boundedness of the RLP \eqref{alp}. We denote an arbitrary solution to the RLP by $\tr_{RLP}$.\par
We now state a useful result from \cite{CS} that characterizes the performance analysis RLP as follows:
\begin{theorem}[Error Bound for RLP]\label{rlpt}
Let $\mu_{u^*}\eqdef(1-\alpha)c^\top (I-\alpha P_{u^*})^{-1}$ be a probability distribution (of discounted number of visits) over the states $S$. Define $\psi_{u^*}$ to be the distribution over the state-action pairs such that $\psi(s,a)\eqdef \frac{\mu_{u^*}}{d}$ and define $\theta\eqdef\frac{1+\alpha}{2 c^\top J^*}\underset{r\in \N}{\sup}\parallel J^*-\Phi r \parallel_\infty$. Then for a given $\epsilon>0$ and $\delta>0$ it holds with probability greater than $1-\delta$ that
\begin{align*}
||J^*-\Phi\tilde{r}_{RLP}||_{1,c}\leq ||J^*-\Phi\tilde{r}||_{1,c}+\epsilon ||J^*||_{1,c}
\end{align*}
for all $m\geq \frac{16d\theta}{(1-\alpha)\epsilon}\big(k\ln\frac{48d\theta}{(1-\alpha)\epsilon}+\ln \frac{2}{\delta}\big)$.
\end{theorem}
The gist of \Cref{rlpt} is that when `sufficient' number of samples are retained using a specialized distribution ($\psi_{u^*}$), then with high probability, the prediction error of RLP and ALP differ only by a small factor (i.e., $\epsilon\norm{J^*}_{1,c}$).\par
A major weakness of \Cref{rlpt} is that it holds only for RLP formulated using $\psi_{u^*}$ which is impractical since $u^*$ is unknown in general. However, empirical studies \cite{ALP,CS,CST} have shown that RLP formulated with other sampling distributions do perform well in experiments. In this context, another interesting approach is linear approximation of the dual variables \cite{dolgov}, which also is known to work in experiments but without any theoretical guarantees. These fact hint to the fact that the theoretical understanding of RLP and constraint sampling/approximation needs to be improved. Further, such theoretical understanding will justify that ALP with constraint reduction is a fully dimensionality free method in that the problem variables as well as constraints are independent of the number of states of the MDP.
\begin{comment}
The Generalized Reduced Linear Program is given as:
\begin{align}\label{grlp}
\begin{split}
&\text{GRLP:~}\underset{r\in \N\subset R^k}{\min}\, \, c^\top \Phi r\,\,\,\,\\
&  \,W^\top E\Phi r\geq W^\top H \Phi r.
\end{split}
\end{align}
\end{comment}
\begin{comment}
\begin{enumerate}

\item In \eqref{mdplp}, \eqref{alp}, \eqref{rlp} and \eqref{grlp} $c>0 \in \R^n$ is a probability distribution.
\item The ALP \eqref{alp} is obtained by making use of LFA in the LP, i.e., by introducing the new variables $r\in \R^k$ and adding the extra constraint $J=\Phi r$ in \eqref{mdplp} with $\Phi \in \R^{n\times k}$ \citep{SchSei85}. Note that in \eqref{alp}, $Phi r\geq T\Phi r$ is a shortcut to denote the $S\times A$ constraints. Also, for $k=n$ and $\Phi=I_{n\times n}$, the ALP is same as the LP. We denote an arbitrary solution to the ALP by $\tr\in \R^k$.\par
\item The RLP \eqref{rlp} was first introduced in \cite{CS}. The RLP \eqref{rlp} has the same objective function as the ALP \eqref{rlp}. The construction of the RLP needs three parameters to be specified namely, the number of samples $m$, the sampling distribution $\psi$ and the constraint set $\N$. In particular, $\psi=\psi(u^*)$ i.e., the sampling distribution
In the RLP in \eqref{rlp}, $\I\subset S \times A$ is the index set of sampled constraints, i.e., $|\I|=m$. The samples are generated using a distribution $\psi$ (see a restatement of the results in \cite{CS} summarized in \Cref{}).
$\N$ is a compact set such that $\tr \in \N$, and it ensures boundedness of the RLP \eqref{alp}. We denote an arbitrary solution to the RLP by $\tr_{RLP}$. It is important to note that the RLP \eqref{rlp} is a random linear program, in the sense that it depends on the $m$ samples obtained from $\psi$.
\item In the GRLP in \eqref{grlp}, $W \in \R^{nd\times m}_+$ is a matrix with all positive entries which specifies the linear combination of constraints. The RLP \eqref{rlp} can be recovered as a special case of the GRLP \cite{grlp} by setting $W$ to the matrix with the $i^{th}$ column having $1$ corresponding to the constraint that was sampled (implicitly assuming that there is a natural ordering of the $nd$ constraints) and all the other entries as $0$. The $\N$ in the RLP \eqref{rlp} is retained in the GRLP \eqref{grlp} as well. For $m=nd$ and $W=I_{nd\times nd}$, the GRLP is same as the ALP. We denote an arbitrary solution to the GRLP by $\hr$.
\end{enumerate}
In what follows, unless specified otherwise we use let $\hj=\Phi \hr$/$\tj=\Phi \tr$ to denote the corresponding value functions and $\hu$/$\tu$ to denote the greedy policy w.r.t. $\hj$/$\tj$.\par
\FloatBarrier
\input{cartoon}
\Cref{cartoon} which shows the solutions to the LP, ALP and GRLP respectively. The error in the ALP solution has already been studied in \cite{ALP}. Our objective is to study the extra source of error due to constraint approximation.
\end{comment}
\begin{comment}
In addition, we answer the following questions related to constraint reduction in ALP that have so far remained open. \\
$\bullet$ As a natural generalization of the RLP, what happens if we define a generalized reduced linear program (GRLP) whose constraints are positive linear combinations of the original constraints of the ALP?\\
$\bullet$ Unlike \cite{CS} which provides error bounds for a specific RLP formulated using an idealized sampling distribution, is it possible to provide error bounds for any GRLP (and hence any RLP)?
In this paper, we address both of the questions above.
\end{comment}

### 2017-02-04 rel.tex
fresh changes

\subsection{Comparison With Related Work}
In order to interpret the resutls in \Cref{cmt2} and \Cref{st}, we now dicuss relevant prior work. We begin by re-stating a preliminary\footnote{The improved error bounds in \cite{ALP} as well as in \Cref{sec:improv} of this paper are in a weighted $L_\infty$ norm and are based on Lyapunov analysis.} error bounds for the ALP from \cite{ALP}:
\begin{theorem}[Error Bound for ALP]\label{alpvanilla}
\begin{align*}
||J^*-\tj||_{1,c}\leq \frac{2}{1-\alpha}\min_{r}||J^*-\Phi r||_\infty
\end{align*}
\end{theorem}
\begin{comment}

The ALP is a linear program in $k$ ($<<n$) variables as opposed to the LP in \eqref{mdplp} which has $n$ variables.
Nevertheless, the ALP has $nd$ constraints (same as the LP) which is an issue when $n$ is large and calls for constraint approximation/reduction techniques.

@@

\end{comment}
%The most important work in the direction of constraint reduction is constraint sampling \cite{CS} wherein a reduced linear program (RLP) is solved instead of the ALP. While the objective of the RLP is same as that of the ALP, the RLP has only $m<<nd$ constraints \emph{sampled} from the original $nd$ constraints of the ALP.
%The following is a preliminary error bound for the RLP from \cite{CS} holds for a special sampling distribution which is dependent on the optimal policy $u^*$ (see \cite{CS} for a detailed presentation):
\begin{theorem}[Error Bound for RLP]\label{rlpt}
If $\tilde{r}_{RLP}$ is a solution to the RLP, then
\begin{align*}
||J^*-\Phi\tilde{r}_{RLP}||_{1,c}\leq ||J^*-\Phi\tilde{r}||_{1,c}+\epsilon ||J^*||_{1,c}
\end{align*}
\end{theorem}
\textbf{Remarks:}
The first factor in the right hand side of \eqref{finalbnd} in \Cref{cmt2} is related to the best possible approximation that can be achieved with the chosen feature matrix $\Phi$. This term is inherent to the ALP formulation as shown in \Cref{alpvanilla}. The second factor in the right hand sie of \eqref{finalbnd} is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy. It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.\par
It is important to note that \Cref{rlpt} holds only in high probability and is valid only under idealized assumption of knowing the optimal policy $u^*$ and \Cref{cmt2} does not have these limitations.
In addition, from \Cref{st}, we know that the additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint approximation is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation. This means that for the RLP to perform well it is enough to retain those states for which the linear function approximation via $\Phi$ is known to perform well.
\begin{comment}
\subsection{Open Questions}
Interestingly, the RLP has nevertheless been found to do well empirically in domain such as Tetris \cite{CST} and controlled queues \cite{CS} even when the constraints were sampled using distribution other than the ideal distribution. This fact indicates a gap in the theoretical analysis and points to the need for a more elaborate theory that addresses the issue of constraint approximation. In this paper, we answer the following questions related to constraint reduction in ALP that have so far remained open. \\
$\bullet$ As a natural generalization of the RLP, what happens if we define a generalized reduced linear program (GRLP) whose constraints are positive linear combinations of the original constraints of the ALP?\\
$\bullet$ Unlike \cite{CS} which provides error bounds for a specific RLP formulated using an idealized sampling distribution, is it possible to provide error bounds for any GRLP (and hence any RLP)?
In this paper, we address both of the questions above.
\end{comment}
\subsection{Primal-Dual Approximation}
The GRLP introduces linear function approximation in both the primal and dual variables of the LP formulation.
To understand this, we need to look at the Lagrangian of the ALP and GRLP in
\eqref{lag} and \eqref{lag2} respectively, i.e.,
\begin{align}\label{lag}
\tilde{L}(r,\lambda)=c^\top \Phi r+\lambda^\top (T\Phi r-\Phi r), \\ \label{lag2}\hat{L}(r,q)=c^\top \Phi r+q^\top W^\top (T\Phi r-\Phi r).
\end{align}
Thus, when $Wq = \lambda$, i.e., when $W$ is a set of basis functions that allow
a low dimensional linear representation of the dual variables $\lambda$,
the two problems are the same.
%Note that $ Wq\approx \lambda$ in \eqref{lag2} is linear function approximation of the Lagrange multipliers.
Hence, while the ALP employs LFA in its objective function (i.e., use of $\Phi r$), the GRLP employs linear approximation both in the objective function ($\Phi r$) as well as the constraints (use of $W$).
%Further, $W$ can be interpreted as the feature matrix that approximates the Lagrange multipliers as $\lambda\approx Wq$, where $\lambda \in \R^{nd}, r\in \R^m$.
To get a sense of how $W$ should be chosen, recall that
the optimal Lagrange multipliers are the discounted number of visits to the ``state-action pairs'' under an optimal policy $u^*$, i.e.,
\begin{align}
\lambda^*(s,u^*(s))&=\big(c^\top(I-\alpha P_{u^*})^{-1}\big)(s)\nn\\
&= \big(c^\top(I+\alpha P_{u^*}+\alpha^2 P_{u^*}^2+\ldots)\big)(s),\nn\\
\lambda^*(s,a)&=0, \qquad \text{for all } a \neq u^*(s),\nn
\end{align}
where $P_{u^*}$ is the probability transition matrix under $u^*$ ($P_{u^*}(s,s') = P_{u^*(s)}(s,s')$, $s,s'\in S$) \cite{dolgov}. Even though we might not have the optimal policy $u^*$ in practice, the fact that $\lambda^*$ is a probability distribution and that it is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$ hints at the kind of features that might be useful for the $W$ matrix.

\begin{comment}
\subsection{Comparison with ADP methods}
A host of the ADP methods such as \cite{lspi,lspe,lstd,Tsit} are based on solving the projected Bellman equation (PBE). The PBE based methods have been empirically successful and also have theoretical guarantees for the approximate value function. However, a significant shortcoming is that they suffer from the issue of \emph{policy-chattering} (see section~$6.4.3$ of \cite{BertB}), i.e., the sequence of policies might oscillate within a set of bad policies. A salient feature of the ALP based methods is that they find only one approximate value function $\tj$ and one sub-optimal policy derived as a greedy policy with respect to $\tj$. As a result there is no such issue of policy-chattering for the ALP based methods. By providing the error bounds for the GRLP, our paper provides the much required theoretical support for the RLP. Our GRLP framework closes the long-standing gap in the literature of providing a theoretical framework to bound the error due to constraint reduction in ALP based schemes.\\

>>>>

\begin{comment}
In order to interpret the results in \Cref{cmt2} and \Cref{st}, we now discuss relevant prior work. We begin by re-stating a preliminary\footnote{The improved error bounds in \cite{ALP} as well as in \Cref{sec:improv} of this paper are in a weighted $L_\infty$ norm and are based on Lyapunov analysis.} error bounds for the ALP from \cite{ALP}:
\begin{theorem}[Error Bound for ALP]\label{alpvanilla}
\begin{align*}
||J^*-\tj||_{1,c}\leq \frac{2}{1-\alpha}\min_{r}||J^*-\Phi r||_\infty
\end{align*}
\end{theorem}
The ALP is a linear program in $k$ ($<<n$) variables as opposed to the LP in \eqref{mdplp} which has $n$ variables.
Nevertheless, the ALP has $nd$ constraints (same as the LP) which is an issue when $n$ is large and calls for constraint approximation/reduction techniques.

@@

%The most important work in the direction of constraint reduction is constraint sampling \cite{CS} wherein a reduced linear program (RLP) is solved instead of the ALP. While the objective of the RLP is same as that of the ALP, the RLP has only $m<<nd$ constraints \emph{sampled} from the original $nd$ constraints of the ALP.
%The following is a preliminary error bound for the RLP from \cite{CS} holds for a special sampling distribution which is dependent on the optimal policy $u^*$ (see \cite{CS} for a detailed presentation):
\begin{theorem}[Error Bound for RLP]\label{rlpt}
Let $\mu_{u^*}\eqdef(1-\alpha)c^\top (I-\alpha P_{u^*})^{-1}$ be a probability distribution (of discounted number of visits) over the states $S$. Define $\psi_{u^*}$ to be the distribution over the state-action pairs such that $\psi(s,a)\eqdef \frac{\mu_{u^*}}{d}$ and define $\theta\eqdef\frac{1+\alpha}{2 c^\top J^*}\underset{r\in \N}{\sup}\parallel J^*-\Phi r \parallel_\infty$. Then for a given $\epsilon>0$ and $\delta>0$ it holds with probability greater than $1-\delta$ that
\begin{align*}
||J^*-\Phi\tilde{r}_{RLP}||_{1,c}\leq ||J^*-\Phi\tilde{r}||_{1,c}+\epsilon ||J^*||_{1,c}
\end{align*}
for all $m\geq \frac{16d\theta}{(1-\alpha)\epsilon}\big(k\ln\frac{48d\theta}{(1-\alpha)\epsilon}+\ln \frac{2}{\delta}\big)$.
\end{theorem}
\end{comment}
\begin{comment}
\subsection{Open Questions}
Interestingly, the RLP has nevertheless been found to do well empirically in domain such as Tetris \cite{CST} and controlled queues \cite{CS} even when the constraints were sampled using distribution other than the ideal distribution. This fact indicates a gap in the theoretical analysis and points to the need for a more elaborate theory that addresses the issue of constraint approximation. In this paper, we answer the following questions related to constraint reduction in ALP that have so far remained open. \\
$\bullet$ As a natural generalization of the RLP, what happens if we define a generalized reduced linear program (GRLP) whose constraints are positive linear combinations of the original constraints of the ALP?\\
$\bullet$ Unlike \cite{CS} which provides error bounds for a specific RLP formulated using an idealized sampling distribution, is it possible to provide error bounds for any GRLP (and hence any RLP)?
In this paper, we address both of the questions above.
\end{comment}
\begin{comment}
\subsection{Comparison with ADP methods}
A host of the ADP methods such as \cite{lspi,lspe,lstd,Tsit} are based on solving the projected Bellman equation (PBE). The PBE based methods have been empirically successful and also have theoretical guarantees for the approximate value function. However, a significant shortcoming is that they suffer from the issue of \emph{policy-chattering} (see section~$6.4.3$ of \cite{BertB}), i.e., the sequence of policies might oscillate within a set of bad policies. A salient feature of the ALP based methods is that they find only one approximate value function $\tj$ and one sub-optimal policy derived as a greedy policy with respect to $\tj$. As a result there is no such issue of policy-chattering for the ALP based methods. By providing the error bounds for the GRLP, our paper provides the much required theoretical support for the RLP. Our GRLP framework closes the long-standing gap in the literature of providing a theoretical framework to bound the error due to constraint reduction in ALP based schemes.\\
